LAGOS lake depth

### 2020-01-01 figures/00_maps.Rmd
add proportion of lakes with max depth by state

# outline <- ne_countries(country = c("canada", "mexico", "united states of america"), 
#                      returnclass = "sf")
# inset_bbox <- mapedit::drawFeatures()
# sf::st_write(inset_bbox, "../data/inset_bbox.gpkg", 
#              layer_options = "OVERWRITE=YES")
# inset_bbox <- st_read("../data/inset_bbox.gpkg")
# outline <- st_crop(outline, inset_bbox)
# outline <- outline %>%
#   st_transform(LAGOSNEgis:::albers_conic()) %>%
#   st_snap(x = ., y = ., tolerance = 0.000001) %>%
#   st_union()

gg_states <- 
  ggplot() + 
    geom_sf(data = study_bbox[2,], alpha = 1, size = 0.6, 
          color = "black", fill = "#1D9DCF") +
    geom_sf(data = states_all, fill = "gray", color = "black", size = 0.3) +
    # geom_sf(data = outline, color = "black", alpha = 0, size = 0.8) +
    # geom_sf(data = hu4, fill = "grey") +
    geom_sf(data = states_focal, fill = "white", color = "black", size = 0.4) + 
    geom_sf(data = dt, aes(color = maxdepth_class), size = 0.6, alpha = 0.8) +
    labs(color = "Max depth (m)") +
    # scale_fill_brewer(palette = "Set2") +
    coord_sf(datum = NA) +
    theme_void()

@@

# gg_hu4 <- 
#   ggplot() + 
#       geom_sf(data = study_bbox, alpha = 1, size = 0.6, 
#               color = "black", fill = "#1D9DCF") +
#       geom_sf(data = states_all, fill = "gray", color = "black", size = 0.3) +
#       geom_sf(data = hu4_focal, fill = "white", color = "black", size = 0.4) +
#       # geom_sf(data = ep, size = 1) +
#       coord_sf(datum = NA) +
#       theme_void() + 
#       theme(legend.position = 0)
# 
# cowplot::plot_grid(gg_states, gg_hu4, ncol = 2, labels = "AUTO", 
#                    vjust = 8, hjust = -1)
```

>>>>

gg_states <- 
  ggplot() + 
    geom_sf(data = study_bbox[2,], alpha = 1, size = 0.6, 
          color = "black", fill = "#1D9DCF") +
    geom_sf(data = states_all, fill = "gray", color = "black", size = 0.3) +
    # geom_sf(data = outline, color = "black", alpha = 0, size = 0.8) +
    # geom_sf(data = hu4, fill = "grey") +
    geom_sf(data = states_focal, fill = "white", color = "black", size = 0.4) + 
    geom_sf(data = dplyr::filter(dt, lake_maxdepth_m < 10), 
            aes(color = maxdepth_class), size = 0.3, alpha = 0.8) +
    geom_sf(data = dplyr::filter(dt, lake_maxdepth_m > 10), 
            aes(color = maxdepth_class), size = 0.45, alpha = 0.8) +
    # scale_color_brewer(palette = "Set1") +
    labs(color = "Max depth (m)") +
    # scale_fill_brewer(palette = "Set2") +
    coord_sf(datum =  NA) +
    theme_void()

@@

```

```{r 00_map_state, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
# proportion of lakes > 4ha with max depth by state
lg <- lagosus_load("locus")
dt <- read.csv("../data/lagosus_depth.csv", stringsAsFactors = FALSE)

dt_plot <- dplyr::select(lg$locus$locus_information, 
                         -contains("decdeg"), 
                         -contains("states"), 
                         -contains("gnis")) %>%
  distinct(lagoslakeid, .keep_all = TRUE) %>%
  left_join(dt, by = "lagoslakeid") %>%
  dplyr::filter(lake_waterarea_ha >= 4) %>%
  group_by(lake_centroidstate) %>%
  summarize(prop_maxdepth = mean(!is.na(lake_maxdepth_m))) %>%
  arrange(desc(prop_maxdepth)) %>%
  left_join(dplyr::filter(
    dplyr::select(states_all, postal, iso_a2), iso_a2 == "US"), 
            by = c("lake_centroidstate" = "postal")) %>%
  dplyr::filter(!is.na(prop_maxdepth))
st_geometry(dt_plot) <- dt_plot$geom

ggplot() + 
  geom_sf(data = dt_plot, aes(fill = prop_maxdepth)) + 
  coord_sf(datum = NA) + theme_void()

```
